Congestion pricing and smart data pricing for networking have been
exteneively studied~\cite{Sen-2013}.
Early work includes congestion pricing by
Murphy {\em et al.}~\cite{Murphy94distributedpricing},
and auction-based resource allocation by
MacKie-Mason {\em et al.}~\cite{pricing-internet-1994}, both in 1994.
Kelly {\em et al.}~\cite{Kelly-1998} framed congestion pricing in an
optimization framework for fair allocation, which inspired a large
number of the following
work~\cite{gibbens1999resource,Henderson2001,Briscoe2003-M3I}.

Congestion pricing are also applied to cloud computing:
For cloud computing services~\cite{Wang-hotcloud2010,Kilcioglu-SIGMETRICS2015},
For cloud computing spot instances~\cite{Song-INFOCOM2017}.

Resource allocation for Edge Computing or Micro Data Centers:
Most approaches use some form of optimization and many employ auction
models.
Zhang {\em et al.}~\cite{Xu2017-zenith,Zhang2017-VMauction}
proposed an online primal-dual optimization for VM auction in IaaS
clouds for welfare and profit maximization.
Distributed resource management for microservices~\cite{Suresh-SOA-SOCC2017}.
load balancing within a data center\cite{Rikhtegar2021BiTEAD,Chen-SOCC-2014}.
pricing used for load-balancing in clouds\cite{Song-2014,Ren-2017}.

Xu {\em et al.}~\cite{Xu2017-zenith} proposed the edge computing
infrastructure layer similar to ours, separating the cloud
infrastructure service from the cloud service for micro datacenters,
but an auction model is proposed for resource allocation.

Exponential cost growth as a function of load is well known in packet
switching networks (e.g., M/M/1 queue and CSMA/CD Ethernet).
We have modified it to make it convex for idle resource pooling, and
exploit it in the pseudo cost function.
A similar idea was found in \cite{Murphy94distributedpricing} where
Murphy {\em et al.} used a cost function for distributed bandwidth
allocation in ATM networks in 1994.
Their cost function is a barrier function for utility optimization
and their simple cost minimizing allocation algorithm is also somewhat
similar to our allocation model.

A system model similar to ours is found in~\cite{Wagner-2012} where
Wagner {\em et al.} used congestion pricing for resilient job
allocation in a distributed millitary cloud.  They used a
game-theoretic resource allocation method based on Nash Bargaining,
and developed a Hadoop-based prototype system.

We were inspired by the concept of micro cloud services to apply packet
switching techniques to distributed heterogeneous clouds, and have
revisited congestion pricing.
To the best of our knowledge, our work is unique in using a convex
cost function for idle-resource pooling.

%%data migration\cite{Pu2015-geodistdata}.
%%distributed data store\cite{Shima2012,Tahoe-2008}.


